### 2018-04-22 Sections/encrypted_cloud_quantum_computing.tex
Deleted algo
Test
Test 2
Displacement key encoding fig

%The Algorithm:Keygen

\begin{algorithm}
\caption{Key Generation algorithm}\label{euclid}
\begin{algorithmic}[1]
\Procedure{KeyGen($\lambda$)}{}
\BState \textbf{Input:} Security parameter $\lambda$
\BState \textbf{Output:} public key $pk$, secret key $sk$
\BState \emph{top}:
\If {$i > \textit{stringlen}$} \Return false
\EndIf
\State $j \gets \textit{patlen}$
\BState \emph{loop}:
\If {$\textit{string}(i) = \textit{path}(j)$}
\State $j \gets j-1$.
\State $i \gets i-1$.
\State \textbf{goto} \emph{loop}.
\State \textbf{close};
\EndIf
\State $i \gets i+\max(\textit{delta}
_1(\textit{string}(i)),\textit{delta}_2(j))$.
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

%
% Blind Computation
%

@@

>>>>

@@

\comment{To do!}
Yes
%
% Blind Computation
%

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{lo_displacement_homo}
\caption{Circuit layout for displacement-key homomorphic encoding of passive linear optics, where \mbox{$\alpha_i'=\alpha_i/r$} and \mbox{$\beta_i'=\beta_i/r$}. Mixing the input modes with respective coherent states on a very low-reflectivity ($r$) beamsplitter implements the displacement operations. Following decoding, the output states is simply given by \mbox{$\ket{\psi_\text{out}} = \hat{U}\ket{\psi_\text{in}}$}, the computed input state.}\label{fig:lo_disp_key_circuit}	
\end{figure}
